#Regression and model validation

The theme for the first exercise is regression analysis.
Data set was survey results from introductory level statistics course, and was about learning approaches.


First the data had to be preprocessed for further analysis. By combining questions in the data, scaling combination variables, and excluding some observations, end result was learning2014.cvs 



```{r}
learning2014 <- read.csv("data/learning2014.csv", header = TRUE, sep=",")

#print out structure of dataset
str(learning2014)
head(learning2014)
```

learning2014.csv consists of 166 observations and 7 variables which are:

* gender
* age
* attitude towards statistics in general
* exam points 

and the three learning approaches 

* deep
* strategic
* surface

##Summary of variables
```{r}
summary(learning2014)
```


##A matrix of scatterplots
```{r}
pairs(learning2014[-1])

```


Age tends to be on the lower side, and there are no clear correlation in any of the pairs. There is interesting gap in the Points variable around value of 15.
```{r}


library(GGally)
library(ggplot2)

ggpairs(learning2014, lower = list(combo = wrap("facethist", bins = 20)))

```


There are no big correlations between variables, biggest being with Attitude and Points (0.437).
Distributions seems quite normally distributed with the exception of Age wich is positively skewed. The gap in the Points variable deforms the distribution some.
```{r}
ggpairs(learning2014, mapping = aes(col = Gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
```

When the data is split with the gender, stronger correlation (-0.622) is found between Deep and Surf variables in the responses of male participants. With female responses this is -0.087.